Intro

### 2019-10-11 doc/Intro.Rmd
small updates for citations-bibliography

>>>>

# Background

## natural variation in RR

empiracal measures -- important / useful for understanding how rec evolves with narutal selection

sources from Ritz Noor,
Samuk et al 2019, (selection,)
(barley in north africa),  Dreissig et al 2019

humans (not very natural population)

## empiracal measures for hetC / theories for evo

Lenormand Duthiel,
Shapley / stapley et al
Sardell Kirkpatrick  
Gruhn + hassold

Hoffman papers -- strange inverted meiosis
Uniparental disomy
-- evidence that RR-constraint connection may be not straight forward.

### lack of female data / sig of female data

human annuploidy / fertility
